Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-10-04 src/tex/ms.tex
Flag point 5 to will

In principle, we should only accept solutions that exactly reproduce the LVK posterior samples in the GW-observable space.
However, it is not feasible to achieve such a condition in practice, therefore we relax the condition in eq.~\ref{eq:loss}
to a small acceptance threshold. For this study, we picked a threshold of $10^{-2}$. To make sure we find a reasonably
complete set of progenitor parameters that corresponds to the posterior sample point, we use 1000 different initial guesses
in solving the optimization problem. As long as the solution fulfills the acceptance criteria, the root is as valid as all
other roots that fulfill the same acceptance criteria, \emph{regardless to its initial guess}.
This means, we have the freedom to choose the set of initial guesses however we think might benefit the optimization.

>>>>

In principle, we should only accept solutions that exactly reproduce the LVK posterior samples in the GW-observable space.
However, it is not feasible to achieve such a condition in practice, therefore we relax the condition in eq.~\ref{eq:loss}
to a small acceptance threshold. For this study, we picked a threshold of $10^{-2}$. To make sure we find a reasonably
complete set of progenitor parameters that corresponds to the posterior sample point, we use 1000 different initial guesses
in solving the optimization problem. As long as the solution fulfills the acceptance criteria, the root is as valid as all
other roots that fulfill the same acceptance criteria, \textbf{\emph{regardless of the initial guess used in finding the root}}.
This means, we have the freedom to choose the set of initial guesses however we think might benefit the optimization.
